---
title: "CSO_HABs"
output: html_document
date: "2024-01-22"
---

Notes When are the lags?

### Library + Data Wrangling

```{r}
#Load the required library 
library(rEDM)
library(tidyverse)
library(googlesheets4)
library(padr)
library(oce)
library(tseries)
library(forecast)
library(spatstat)
library(tseries)
library(corrplot)
library(lubridate)
library(psych)
library(Hmisc)
library(mgcv)


```

### MWRA CSO Data

```{r}

MWRACSOData2016 <- read_sheet('https://docs.google.com/spreadsheets/d/1BF5lMyYrnILoS-rySwTGILiaqYfxA5-Pz5P2xUmOIq8/edit?usp=sharing')

MWRACSOData <- read_sheet('https://docs.google.com/spreadsheets/d/1PRu1yvIuxOnMyazAVkXGv7dkOKUClNxl7CrvrctPREU/edit?usp=sharing')



```

```{r}


#Extract Date
MWRACSOData$Date <- as.Date(MWRACSOData$`Start Time`, format = "%m/%d/%Y")


#Remove Excess Charecters

#Remove "Treated" in Volume Column
MWRACSOData$`Volume (MG)` <- gsub("Treated","",as.character(MWRACSOData$`Volume (MG)`))

#Remove "min" in Minutes Column

MWRACSOData$Minutes <- gsub("min","",as.character(MWRACSOData$Minutes))

#Remove Rows w/ "*"
MWRACSOData <- MWRACSOData %>% filter(!grepl("\\*", MWRACSOData$Duration))

#Replace NA w/ 0
MWRACSOData$Minutes[is.na(MWRACSOData$Minutes)] <- 0

#Make Duration Column
MWRACSOData$Minutes <- as.numeric(MWRACSOData$Minutes)
MWRACSOData$Hours <- as.numeric(MWRACSOData$Hours)

MWRACSOData$CombinedMinutes <- MWRACSOData$Minutes + (MWRACSOData$Hours * 60)

#Remove Columns 

MWRACSOData <- MWRACSOData[-c(4:10)]

#Check Dates

unique_dates <- unique(MWRACSOData$Date)


# Sanity Check: CombinedMinutes to numeric and Date to Date format
MWRACSOData <- MWRACSOData %>%
  mutate(CombinedMinutes = as.numeric(CombinedMinutes),
         Date = as.Date(Date))

MWRACSOData <- MWRACSOData %>%
  mutate(`Volume (MG)` = as.numeric(`Volume (MG)`),
         Date = as.Date(Date))

# Group by Date and calculate the sum of CombinedMinutes



MWRACSOData2 <- 
aggregate(MWRACSOData$CombinedMinutes, by=list(MWRACSOData$Date, MWRACSOData$`Outfall Location`), FUN = sum) 


MWRACSOData3 <- 
aggregate(MWRACSOData$`Volume (MG)`, by=list(MWRACSOData$Date, MWRACSOData$`Outfall Location`), FUN = sum) 

MWRACSOData20162 <- 
aggregate(MWRACSOData2016$`Duration (Min)`, by=list(MWRACSOData2016$Date, MWRACSOData2016$CSOName), FUN = sum) 

MWRACSOData20163 <- 
aggregate(MWRACSOData2016$`Volume (MG)`, by=list(MWRACSOData2016$Date, MWRACSOData2016$CSOName), FUN = sum) 


# Rename a column using colnames

colnames(MWRACSOData2)[1:3] <- c("Date","Outfall Location", "Total Minutes")

colnames(MWRACSOData20162)[1:3] <- c("Date","Outfall Location", "Total Minutes")

colnames(MWRACSOData3)[1:3] <- c("Date","Outfall Location", "Volume")

colnames(MWRACSOData20163)[1:3] <- c("Date","Outfall Location", "Volume")

#Set Columns to Be The Same

MWRACSOData <- MWRACSOData[-c(1,4,5,7)]

MWRACSOData2016 <- MWRACSOData2016[-c(3:8)]




#Make New Names

MWRA_new_names <- c(
  "CSO_ID",
  "Outfall Location",
  "Date"
)

MWRA2016_new_names <- c(
  "CSO_ID",
  "Outfall Location",
  "Date"
)

MWRACSOData <- MWRACSOData %>% 
  set_names(MWRA_new_names)
  
MWRACSOData2016 <- MWRACSOData2016 %>% 
  set_names(MWRA2016_new_names)

#Fix Date Format

MWRACSOData$Date <- format(as.Date(MWRACSOData$Date, format=
                           "%Y-%m-%d"          ), "%m-%d-%Y")

#Merge Columns 

MergedMWRACSO <- rbind(MWRACSOData,MWRACSOData2016)

#Order Date

MergedMWRACSO[order(as.Date(MergedMWRACSO$Date, format="%m/%d/%Y")),]

#Fix Date Formats of Future Joins
MWRACSOData2$Date <- format(as.Date(MWRACSOData2$Date, format=
                           "%Y-%m-%d"          ), "%m-%d-%Y")


MWRACSOData3$Date <- format(as.Date(MWRACSOData3$Date, format=
                           "%Y-%m-%d"          ), "%m-%d-%Y")

# Perform the joins

MergedMWRACSO <- merge(MergedMWRACSO, MWRACSOData2[, c("Date", "Outfall Location", "Total Minutes")], 
                       by.x = c("Date", "Outfall Location"), 
                       by.y = c("Date", "Outfall Location"), all.x = TRUE)

MergedMWRACSO <- merge(MergedMWRACSO, MWRACSOData20162[, c("Date", "Outfall Location", "Total Minutes")], 
                       by.x = c("Date", "Outfall Location"), 
                       by.y = c("Date", "Outfall Location"), all.x = TRUE)

# Combine the columns using coalesce
MergedMWRACSO <- MergedMWRACSO %>%
  mutate(TotalMinutes_combined = coalesce(`Total Minutes.x`, `Total Minutes.y`))


# Drop the individual columns if you no longer need them
MergedMWRACSO <- MergedMWRACSO %>%
  select(-`Total Minutes.x`, -`Total Minutes.y`)


MergedMWRACSO <- merge(MergedMWRACSO, MWRACSOData3[, c("Date", "Outfall Location", "Volume")], 
                       by.x = c("Date", "Outfall Location"), 
                       by.y = c("Date", "Outfall Location"), all.x = TRUE)

MergedMWRACSO <- merge(MergedMWRACSO, MWRACSOData20163[, c("Date", "Outfall Location", "Volume")], 
                       by.x = c("Date", "Outfall Location"), 
                       by.y = c("Date", "Outfall Location"), all.x = TRUE)

MergedMWRACSO <- MergedMWRACSO %>%
  mutate(Volume_combined = coalesce(`Volume.x`, `Volume.y`))


# Drop the individual columns if you no longer need them
MergedMWRACSO <- MergedMWRACSO %>%
  select(-`Volume.x`, -`Volume.y`)


```

```{r}

MWRACSOCoords <- read_sheet('https://docs.google.com/spreadsheets/d/1O9RONCW0lGEsPrt-srZU8M4xeNxDM3hJmkA1IWL2mW4/edit?usp=sharing')

MWRACSOCoords2 <- read_sheet('https://docs.google.com/spreadsheets/d/18PK0CcX6Ye5RZJtVUI8mmiaRwLIpRNIzGCwOupSqf-k/edit?usp=sharing')


```

```{r}

MWRACSOFinal <-  
left_join(MergedMWRACSO , MWRACSOCoords ,  by = c("CSO_ID" = "OUTFALL"  ))

#MWRACSOCoords2$OUTFALL_ID <- as.character(MWRACSOCoords2$OUTFALL_ID )

#MWRACSOFinal <-  
#left_join(MergedMWRACSO , MWRACSOCoords2 ,  by = c("CSO_ID" = "OUTFALL_ID"  ))
```

```{r}
write_csv(MWRACSOFinal, file = "MWRACSOs.csv") 
```

```{r}
# List all objects in the environment
all_objects <- ls()

# Identify objects to keep
objects_to_keep <- c("MWRACSOFinal")

# Identify objects to remove
objects_to_remove <- setdiff(all_objects, objects_to_keep)

# Remove unwanted objects
rm(list = objects_to_remove)

rm(all_objects)
rm(objects_to_keep)
rm(objects_to_remove)

```

###Get Phy

```{r}
#Charles River
#Reads data into R
CR2023 <- read_sheet('https://docs.google.com/spreadsheets/d/1R_HdqGuVMlfRyVPCzOw3CvbOjXDQfzFtDCMvKdj5vXU/edit?usp=sharing')

CR2022 <- read_sheet('https://docs.google.com/spreadsheets/d/1equdXHt4d-2s3r8YSsuHfpLufeRmGqno-SJqhcEwuNY/edit?usp=sharing')

CR2021 <- read_sheet('https://docs.google.com/spreadsheets/d/1CBzAD9uot_SPkY-JV-lJB6FSxSjlgXIS8A4jSY9SJjE/edit?usp=sharing')

CR2020 <- read_sheet('https://docs.google.com/spreadsheets/d/1fOV7JfJwLxddCaTsR0vkUodOZup4Y6HwVthMLzexe-I/edit?usp=sharing')

CR2019 <- read_sheet('https://docs.google.com/spreadsheets/d/1WGTUQ7F8wadO4RJ6PsfRsEnvwqNMdnAsdX71xqI9L-4/edit?usp=sharing')

CR2018 <- read_sheet('https://docs.google.com/spreadsheets/d/17AX8HNLXUCYz6YJIHRnb_rrKuzDudyAEq5WEhbSxOFQ/edit?usp=sharing')

CR2017 <- read_sheet('https://docs.google.com/spreadsheets/d/18xDJ9cLaZuj3JqhFsf847nSLMGKjfvWZmHWifsrPBq8/edit?usp=sharing')

CR2016 <- read_sheet('https://docs.google.com/spreadsheets/d/1rEOGM2H9cgVbFgVkIQZjIyzzl03fIywtkxBNg7GmXrY/edit?usp=sharing')

CR2015 <- read_sheet('https://docs.google.com/spreadsheets/d/11I8RQnOgZ9xmVEpaTVM_ELQZdTTp6T_305nwxkNI92I/edit?usp=sharing')

#Prints the data
```

```{r}
#bind rows
df_CR <- bind_rows(
  CR2015,
  CR2016,
  CR2017, 
  CR2018,
  CR2019,
  CR2020,
  CR2021,
  CR2022,
  CR2023
)
#combine data
df_CR <- df_CR %>%
  mutate(hour = pmin(hour(`time est`),hour(`time edt`),na.rm=T),
         minute = pmin(minute(`time est`),minute(`time edt`),na.rm=T)) %>%
  select(date,hour,minute,chl=`chlorophyll (rfu)`,phy=`phycocyanin (rfu)`, ph=`ph`, Celsius =`temp c`,  spcond = `spcond (ms/cm)`, do = `do (mg/l)`,turb = `turbidity (fnu)` )
  
#%>% rename(`time est`=time)

```

#Aggregate Values Daily

```{r}
df_CR$Salinity <- 

  swSCTp(
  df_CR$spcond,
df_CR$Celsius,
  pressure = rep(10.1325,NROW(df_CR)),
  # "mS/cm",
"",
  eos = getOption("oceEOS", default = "gsw")
)


ag_df_CR <-df_CR %>%
   group_by(date) %>%
  summarise(chl=mean(chl), phy=mean(phy), ph=mean(ph), Celsius=mean(Celsius), spcond=mean(spcond), do=mean(do), turb=mean(turb), Salinity = mean(Salinity))

```

LM and GAM relaxes linearity can say wether term is linear or spline whether error distribution is

Difference between GAM and LM is GAM works with non gaussion can use GAM to fit GM by saying distribution is normal whether response variable is linear or non-linear

GAM - put variable where non linear x

###CAMCSO

```{r}

CAM2015CSO <- read_sheet('https://docs.google.com/spreadsheets/d/11v15YsnizQBilaTK-mzJWz-qp1PLJGqQwrxQ2AV7WdA/edit?usp=sharing', sheet = '2015CAMCSO')


CAM2016CSO <- read_sheet('https://docs.google.com/spreadsheets/d/11v15YsnizQBilaTK-mzJWz-qp1PLJGqQwrxQ2AV7WdA/edit?usp=sharing', sheet = '2016CAMCSO')

CAM2016CSO <- subset(CAM2016CSO, select = c("Date", "CAM017* (MG)"))



CAM2017CSO <- read_sheet('https://docs.google.com/spreadsheets/d/11v15YsnizQBilaTK-mzJWz-qp1PLJGqQwrxQ2AV7WdA/edit?usp=sharing', sheet = '2017CAMCSO')


CAM2017CSO <- subset(CAM2017CSO, select = c("Date", "CAM017* (MG)"))




CAM2018CSO <- read_sheet('https://docs.google.com/spreadsheets/d/11v15YsnizQBilaTK-mzJWz-qp1PLJGqQwrxQ2AV7WdA/edit?usp=sharing', sheet = '2018CAMCSO')


CAM2018CSO <- subset(CAM2018CSO, select = c("Date", "CAM017* (MG)"))

CAM2019CSO <- read_sheet('https://docs.google.com/spreadsheets/d/11v15YsnizQBilaTK-mzJWz-qp1PLJGqQwrxQ2AV7WdA/edit?usp=sharing', sheet = '2019CAMCSO')



CAM2019CSO <- subset(CAM2019CSO, select = c("Date", "CAM017* (MG)"))

CAM2020CSO <- read_sheet('https://docs.google.com/spreadsheets/d/11v15YsnizQBilaTK-mzJWz-qp1PLJGqQwrxQ2AV7WdA/edit?usp=sharing', sheet = '2020CAMCSO')


CAM2020CSO <- subset(CAM2020CSO, select = c("Date", "CAM017* (MG)"))

CAM2021CSO <- read_sheet('https://docs.google.com/spreadsheets/d/11v15YsnizQBilaTK-mzJWz-qp1PLJGqQwrxQ2AV7WdA/edit?usp=sharing', sheet = '2021CAMCSO')


CAM2021CSO <- subset(CAM2021CSO, select = c("Date", "CAM017* (MG)"))

CAM2022CSO <- read_sheet('https://docs.google.com/spreadsheets/d/11v15YsnizQBilaTK-mzJWz-qp1PLJGqQwrxQ2AV7WdA/edit?usp=sharing', sheet = '2022CAMCSO')

CAM2022CSO <- subset(CAM2022CSO, select = c("Date", "CAM017* (MG)"))


```

```{r}
# Combine all values into a single vector and sort them

library(dplyr)

# Ensure column names are consistent across all data frames
colnames(CAM2015CSO) <- c("Date", "CAM017* (MG)")
colnames(CAM2016CSO) <- c("Date", "CAM017* (MG)")
colnames(CAM2017CSO) <- c("Date", "CAM017* (MG)")
colnames(CAM2018CSO) <- c("Date", "CAM017* (MG)")
colnames(CAM2019CSO) <- c("Date", "CAM017* (MG)")
colnames(CAM2020CSO) <- c("Date", "CAM017* (MG)")
colnames(CAM2021CSO) <- c("Date", "CAM017* (MG)")
colnames(CAM2022CSO) <- c("Date", "CAM017* (MG)")

CAM2015CSO$`CAM017* (MG)` <- as.numeric(CAM2015CSO$`CAM017* (MG)`)
CAM2016CSO$`CAM017* (MG)` <- as.numeric(CAM2016CSO$`CAM017* (MG)`)
CAM2017CSO$`CAM017* (MG)` <- as.numeric(CAM2017CSO$`CAM017* (MG)`)
CAM2018CSO$`CAM017* (MG)` <- as.numeric(CAM2018CSO$`CAM017* (MG)`)
CAM2019CSO$`CAM017* (MG)` <- as.numeric(CAM2019CSO$`CAM017* (MG)`)
CAM2020CSO$`CAM017* (MG)` <- as.numeric(CAM2020CSO$`CAM017* (MG)`)
CAM2021CSO$`CAM017* (MG)` <- as.numeric(CAM2021CSO$`CAM017* (MG)`)
CAM2022CSO$`CAM017* (MG)` <- as.numeric(CAM2022CSO$`CAM017* (MG)`)


# Make sure that the "CAM017* (MG)" column is of type double


CAM017 <- bind_rows(
 CAM2016CSO,
  CAM2017CSO, 
  CAM2018CSO,
  CAM2019CSO,
  CAM2020CSO,
  CAM2021CSO,
  CAM2022CSO,
)


CAM017 <- CAM017 %>% rename(MG = `CAM017* (MG)`)

CAM017_discharges <- subset(CAM017, MG != 0)



```

### ALL CSOs

```{r}

ag_df_CR$Date <- ag_df_CR$date

ag_df_CR <- ag_df_CR[,-c(1) ]

#rm(CR2023, CR2022, CR2020, CR2021, CR2020, CR2019, CR2018, CR2017, CR2016, CR2015, df_CR)

ag_df_CR2 <- ag_df_CR


#Fix Date Formats of Future Joins
MWRACSOFinal$Date <- format(as.Date(MWRACSOFinal$Date, format=
                           "%m-%d-%Y"         ), "%m-%d-%Y")


ag_df_CR2$Date <- format(as.Date(ag_df_CR2$Date , format=
                           "%Y-%m-%d"          ), "%m-%d-%Y")


#join

All <- merge(MWRACSOFinal, ag_df_CR2, by = "Date", all = TRUE)

# Assuming your date column is named "Date"
All$Date <- as.Date(All$Date, format="%m-%d-%Y")

# Order the data frame by Year, Month, and Day
All <- All[order(year(All$Date), month(All$Date), day(All$Date)), ]

```

Join CAM + CSO

```{r}
All <- merge(All, CAM017, by = "Date", all = TRUE)
All <- All %>%
  rename(CAM017MG = MG)
```

###CSO OCCURRANCES

```{r}

# Assuming your data frame is named MWRACSOFinal and the column with CSO IDs is named CSO_ID
cso_counts <- as.data.frame(table(MWRACSOFinal$CSO_ID))

#011

```

###Noteworthy Points MWR203 MWRA Charles/Boston Harbor MWR205 MWRA Mystic MWR201 MWRA Cottage Farm MWR021 Close to Buoy, MWRA

### SINGLE BEST POINT

```{r}

#MWR203 MWRA Charles/Boston Harbor 
#MWR205 MWRA Mystic
#MWR201 MWRA Cottage Farm
#MWR021 Close to Buoy, MWRA
#CAM017 best CAM point  


Single_best <- All[All$CSO_ID == "MWR203", ]
#this removes all rows that are not MWR203 

```

GAM - Gaussian

```{r}
#CAM017 as best point 
library(mgcv)

# Assuming All is your dataset
GAM_Single <- gam(phy ~ s(CAM017MG), family = gaussian, data = All, method = "REML")
GAM_Single
plot(GAM_Single)

```

GAM - Gamma

```{r}
# Assuming GAM_Single is your GAM model object
GAM_Single <- gam(phy ~ s(CAM017MG), family = Gamma(link = "log"), data = All, method = "REML")
GAM_Single
plot(GAM_Single)
```

**Error in eval(family\$initialize) : non-positive values not allowed for the 'Gamma' family**

GLM

```{r}
# Assuming All is your dataset
glm_single <- glm(phy ~ CAM017MG, family = gaussian, data = All)

# Summary of the GLM model
summary(glm_single)

plot(glm_single)
```

### BEST COUPLE

```{r}

Couple_best <- All[All$CSO_ID %in% c("MWR203", "MWR201"), ]

```

### Interpolated

```{r}
#Step 1: Plot the Data
plot(y ~ x)

#OLS using the lm function 
model = lm((y ~ x))
summary(model)

#OLS using GLM
model.glm = glm(y ~ x, family = gaussian(link = "identity"))
summary(model.glm)
```

use gaussian or gamma, not count \### GLM (Generalized Linear Model)

family(object, ...)

binomial(link = "logit") gaussian(link = "identity")

Gamma(link = "inverse") 0 bound contious distribution page 79

inverse.gaussian(link = "1/mu\^2") poisson(link = "log") quasi(link = "identity", variance = "constant") quasibinomial(link = "logit") quasipoisson(link = "log")

What Do I Chose Here?

### GAM (Generalized Additive Model)

GAM has same choice of families specify what varaibles you want to be smoothed MGCV package challenge2021_manuscript.Rmd put s what you want to be splined method REML default add family if you want

```{r}
library(gam)

#model <- gam( y ~ x, data = , method = " f " ) 




```

### Interpolate all Data into one point

### Analysis of Fit

### 6.2 Spatial Viability

### 6.2 A Calculate correlations among locations for loop

### 6.2 B GLM (Generalized Linear Model)

### 6.3 C GAM (Generalized Additive Model)

### 6.4 Gap filled predicted mean
