---
title: "EPABuoyCharles"
output: html_document
date: "2023-10-18"
---
```{r}
  #Install the required package
install.packages('googlesheets4')
```
```{r}
# Install from CRAN
install.packages("tidyverse")
install.packages("lubridate")
```

```{r}
#Load the required library 
library(googlesheets4)
```

```{r}
#Read google sheets data into R
x <- read_sheet('https://docs.google.com/spreadsheets/d/1J9-ZpmQT_oxLZ4kfe5gRvBs7vZhEGhSCIpNS78XOQUE/edit?usp=sharing')
```
#Charles River
```{r}
#Reads data into R
CR2023 <- read_sheet('https://docs.google.com/spreadsheets/d/1R_HdqGuVMlfRyVPCzOw3CvbOjXDQfzFtDCMvKdj5vXU/edit?usp=sharing')

CR2022 <- read_sheet('https://docs.google.com/spreadsheets/d/1equdXHt4d-2s3r8YSsuHfpLufeRmGqno-SJqhcEwuNY/edit?usp=sharing')

CR2021 <- read_sheet('https://docs.google.com/spreadsheets/d/1CBzAD9uot_SPkY-JV-lJB6FSxSjlgXIS8A4jSY9SJjE/edit?usp=sharing')

CR2020 <- read_sheet('https://docs.google.com/spreadsheets/d/1fOV7JfJwLxddCaTsR0vkUodOZup4Y6HwVthMLzexe-I/edit?usp=sharing')

CR2019 <- read_sheet('https://docs.google.com/spreadsheets/d/1WGTUQ7F8wadO4RJ6PsfRsEnvwqNMdnAsdX71xqI9L-4/edit?usp=sharing')

CR2018 <- read_sheet('https://docs.google.com/spreadsheets/d/17AX8HNLXUCYz6YJIHRnb_rrKuzDudyAEq5WEhbSxOFQ/edit?usp=sharing')

CR2017 <- read_sheet('https://docs.google.com/spreadsheets/d/18xDJ9cLaZuj3JqhFsf847nSLMGKjfvWZmHWifsrPBq8/edit?usp=sharing')

CR2016 <- read_sheet('https://docs.google.com/spreadsheets/d/1rEOGM2H9cgVbFgVkIQZjIyzzl03fIywtkxBNg7GmXrY/edit?usp=sharing')

CR2015 <- read_sheet('https://docs.google.com/spreadsheets/d/11I8RQnOgZ9xmVEpaTVM_ELQZdTTp6T_305nwxkNI92I/edit?usp=sharing')

#Prints the data

```

```{r}
df_CR <- bind_rows(
  CR2015,
  CR2016,
  CR2017 %>% rename(`time est`=time),
  CR2018,
  CR2019,
  CR2020,
  CR2021,
  CR2022,
  CR2023
)

df_CR <- df_CR %>%
  mutate(hour = pmin(hour(`time est`),hour(`time edt`),na.rm=T),
         minute = pmin(minute(`time est`),minute(`time edt`),na.rm=T)) %>%
  select(date,hour,minute,chl=`chlorophyll (rfu)`,phy=`phycocyanin (rfu)`)
  
```


```{r}
#Create Missing Hours + Insert NA Values 
library(dplyr, warn.conflicts = FALSE)
library(tidyr)

#df_CR_all <- tribble(
 # ~timestamp,
  #"6/4/2012 2:00",
  #"6/4/2012 3:00",
  #"6/4/2012 12:00",
  #"6/4/2012 13:00",
  #"6/4/2012 16:00",
  #"6/4/2012 20:00",
  #"6/4/2012 22:00",
  #"6/4/2012 23:00",
  #"6/5/2012 3:00",
  #"6/5/2012 15:00",
  #"6/5/2012 20:00",
  #"6/6/2012 2:00"
#)

#df_CR_all <- mutate(df_CR_all, timestamp = as.POSIXct(timestamp, format = "%m/%d/%Y %H:%M"))

df_CR_all <- complete(df_CR, timestamp = seq.POSIXt(min(timestamp), max(timestamp), by = "hour", "pairwise")
df_CR_all
```



```{r}
df_CR %>% group_by(date,hour) %>%
  filter(year(date) >= 2021) %>%
  summarise(across(c("chl","phy"),mean),.groups="keep") %>%
  mutate(date= date+hours(hour)) %>%
  ggplot(aes(x=date)) + 
  geom_path(aes(y=chl,color="chl")) + 
  geom_path(aes(y=phy,color="phy"))
```


```{r}
ts_chl_2021 <- df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(chl)

ts_phy_2021 <- df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(phy)


length(ts_chl_2021)
acf(ts_chl_2021,lag.max = 24*30)
acf(ts_phy_2021,lag.max = 24*30)
```


```{r}
ts_chl_2021 <- df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(chl)

ts_phy_2021 <- df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(phy)


length(ts_chl_2021)
acf(ts_chl_2021,lag.max = 30)
acf(ts_phy_2021,lag.max = 30)

## you can check an individual value as follows
cor(ts_phy_2021,lag(ts_phy_2021,6),use="pairwise")

```

#Mystic
```{r}

#Reads data into R
MR2023 <- read_sheet('https://docs.google.com/spreadsheets/d/1R_HdqGuVMlfRyVPCzOw3CvbOjXDQfzFtDCMvKdj5vXU/edit?usp=sharing')

MR2022 <- read_sheet('https://docs.google.com/spreadsheets/d/1equdXHt4d-2s3r8YSsuHfpLufeRmGqno-SJqhcEwuNY/edit?usp=sharing')

MR2021 <- read_sheet('https://docs.google.com/spreadsheets/d/1Plw_zpnRmz6vs3ZyhHr88M1PX3GAQMvBnVv6cKgM5hk/edit?usp=sharing')

#MR2020 does not exist

MR2019 <- read_sheet('https://docs.google.com/spreadsheets/d/1rVk7lLEXyA7nOzjmszhe1cjYGeGkG_pgfDdC_XsDojs/edit?usp=sharing')

MR2018 <- read_sheet('https://docs.google.com/spreadsheets/d/14mxyMMuZvD38kcb-4Xk9APvnY-1z95czcckXm_Dyg_w/edit?usp=sharing')

MR2017 <- read_sheet('https://docs.google.com/spreadsheets/d/1fDgZrK7rcXdpvcCyZZWT0TrpIFcDwJ1ZE5v2yHYJo7U/edit?usp=sharing')

MR2016 <- read_sheet('https://docs.google.com/spreadsheets/d/17eNCkZNgf6aouqLVN8TEPodX4OGDFitxjBb8rapQiJ8/edit?usp=sharing')

MR2015 <- read_sheet('https://docs.google.com/spreadsheets/d/1JA_MWcbTwdW2oVO9ee1TrbhbYx03wN8MXgFZRMvyyWw/edit?usp=sharing')

#Prints the data

```
```{r}
df_MR <- bind_rows(
  MR2015,
  MR2016,
  MR2017 %>% rename(`time est`=time),
  MR2018,
  MR2019,
  MR2021,
  MR2022,
  MR2023
)

df_MR <- df_MR %>%
  mutate(hour = pmin(hour(`time est`),hour(`time edt`),na.rm=T),
         minute = pmin(minute(`time est`),minute(`time edt`),na.rm=T)) %>%
  select(date,hour,minute,chl=`chlorophyll (rfu)`,phy=`phycocyanin (rfu)`)

```


```
```{r}
df_MR %>% group_by(date,hour) %>%
  filter(year(date) >= 2021) %>%
  summarise(across(c("chl","phy"),mean),.groups="keep") %>%
  mutate(date= date+hours(hour)) %>%
  ggplot(aes(x=date)) + 
  geom_path(aes(y=chl,color="chl")) + 
  geom_path(aes(y=phy,color="phy"))
```


```{r}
ts_chl_2021 <- df_MR %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(chl)

ts_phy_2021 <- df_MR %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(phy)


length(ts_chl_2021)
acf(ts_chl_2021,lag.max = 24*30)
acf(ts_phy_2021,lag.max = 24*30)
```


```{r}
ts_chl_2021 <- df_MR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(chl)

ts_phy_2021 <- df_MR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(phy)


length(ts_chl_2021)
acf(ts_chl_2021,lag.max = 30)
acf(ts_phy_2021,lag.max = 30)

## you can check an individual value as follows
cor(ts_phy_2021,lag(ts_phy_2021,6),use="pairwise")

