---
title: "HAB_CCM"
output: html_document
date: "2024-02-01"
---
###Get Phy

```{r}
library(tidyverse)
library(googlesheets4)
library(oce)
library(padr)
library(rEDM)
library(ggplot2)

```

```{r}
#Charles River
#Reads data into R
CR2023 <- read_sheet('https://docs.google.com/spreadsheets/d/1R_HdqGuVMlfRyVPCzOw3CvbOjXDQfzFtDCMvKdj5vXU/edit?usp=sharing')

CR2022 <- read_sheet('https://docs.google.com/spreadsheets/d/1equdXHt4d-2s3r8YSsuHfpLufeRmGqno-SJqhcEwuNY/edit?usp=sharing')

CR2021 <- read_sheet('https://docs.google.com/spreadsheets/d/1CBzAD9uot_SPkY-JV-lJB6FSxSjlgXIS8A4jSY9SJjE/edit?usp=sharing')

CR2020 <- read_sheet('https://docs.google.com/spreadsheets/d/1fOV7JfJwLxddCaTsR0vkUodOZup4Y6HwVthMLzexe-I/edit?usp=sharing')

CR2019 <- read_sheet('https://docs.google.com/spreadsheets/d/1WGTUQ7F8wadO4RJ6PsfRsEnvwqNMdnAsdX71xqI9L-4/edit?usp=sharing')

CR2018 <- read_sheet('https://docs.google.com/spreadsheets/d/17AX8HNLXUCYz6YJIHRnb_rrKuzDudyAEq5WEhbSxOFQ/edit?usp=sharing')

CR2017 <- read_sheet('https://docs.google.com/spreadsheets/d/18xDJ9cLaZuj3JqhFsf847nSLMGKjfvWZmHWifsrPBq8/edit?usp=sharing')

CR2016 <- read_sheet('https://docs.google.com/spreadsheets/d/1rEOGM2H9cgVbFgVkIQZjIyzzl03fIywtkxBNg7GmXrY/edit?usp=sharing')

CR2015 <- read_sheet('https://docs.google.com/spreadsheets/d/11I8RQnOgZ9xmVEpaTVM_ELQZdTTp6T_305nwxkNI92I/edit?usp=sharing')

#Prints the data
```

```{r}
#bind rows
df_CR <- bind_rows(
  CR2015,
  CR2016,
  CR2017, 
  CR2018,
  CR2019,
  CR2020,
  CR2021,
  CR2022,
  CR2023
)
#combine data
df_CR <- df_CR %>%
  mutate(hour = pmin(hour(`time est`),hour(`time edt`),na.rm=T),
         minute = pmin(minute(`time est`),minute(`time edt`),na.rm=T)) %>%
  select(date,hour,minute,chl=`chlorophyll (rfu)`,phy=`phycocyanin (rfu)`, ph=`ph`, Celsius =`temp c`,  spcond = `spcond (ms/cm)`, do = `do (mg/l)`,turb = `turbidity (fnu)` )
  
#%>% rename(`time est`=time)

```


#Aggregate Values Daily
```{r}
df_CR$Salinity <- 

  swSCTp(
  df_CR$spcond,
df_CR$Celsius,
  pressure = rep(10.1325,NROW(df_CR)),
  # "mS/cm",
"",
  eos = getOption("oceEOS", default = "gsw")
)


ag_df_CR <-df_CR %>%
   group_by(date) %>%
  summarise(chl=mean(chl), phy=mean(phy), ph=mean(ph), Celsius=mean(Celsius), spcond=mean(spcond), do=mean(do), turb=mean(turb), Salinity = mean(Salinity))

```

### First Diff Phy

```{r}
ag_df_CR <- ag_df_CR %>% pad %>%
mutate(del_phy = phy - lag(phy,1))
 ag_df_CR %>% ggplot(aes(x=date,y=del_phy)) + geom_line()

```




###Library 

#```{r}

#Without NA Values

#morndf_CR <- na.omit(morndf_CR) 


# Find the first row number for the first date in 2023
first_row_2023 <- which(format(morndf_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

# Find the last value 
last_value <- nrow(morndf_CR)

print(last_value)

```


#```{r}
lib_ins <- c() 
#  String of 3 whitespace separated integer values specifying the intial library size; the final library size; and the library size increment for CCM.

sample <- 
  #Integer specifying the number of random samples to draw at each library size evaluation for CCM.

```


###LOGAN 
```{r}

Logan <- read_sheet('https://docs.google.com/spreadsheets/d/1h3mNXsGZxB4fhkZQGr2e8z6CxAQtumA5a208-GEYvBw/edit?usp=sharing')

# Convert to POSIXct object
Logan$DATE <- as.POSIXct(Logan$DATE, format = "%Y-%m-%dT%H:%M:%S")

Logan2 <- Logan

# Remove "s" suffixes from HourlyAltimeterSetting column
Logan2$HourlyAltimeterSetting <- gsub("s$", "", Logan$HourlyAltimeterSetting)

# Convert HourlyAltimeterSetting to numeric
Logan$HourlyAltimeterSetting <- as.numeric(Logan$HourlyAltimeterSetting)



# Convert columns to numeric (excluding DATE)
numeric_cols <- c("HourlyAltimeterSetting", "HourlyDewPointTemperature", "HourlyDryBulbTemperature",
                  "HourlyPrecipitation", "HourlyPressureChange", "HourlyPressureTendency",
                  "HourlyRelativeHumidity", "HourlySeaLevelPressure", "HourlyStationPressure",
                  "HourlyVisibility", "HourlyWetBulbTemperature", "HourlyWindDirection",
                  "HourlyWindGustSpeed", "HourlyWindSpeed")

Logan <- Logan %>%
  mutate(across(all_of(numeric_cols), as.numeric))








Logan$HourlySeaLevelPressure <- gsub("s$", "", Logan$HourlySeaLevelPressure)







ag_Logan <- Logan %>%
  group_by(DATE) %>%
  summarise(
    HourlyAltimeterSetting = mean(HourlyAltimeterSetting),
    HourlyDewPointTemperature = mean(HourlyDewPointTemperature),
    HourlyDryBulbTemperature = mean(HourlyDryBulbTemperature), 
    HourlyPrecipitation = sum(HourlyPrecipitation),
    HourlyPressureChange = mean(HourlyPressureChange),
    HourlyPressureTendency = mean(HourlyPressureTendency),
    HourlyRelativeHumidity = mean(HourlyRelativeHumidity), 
    HourlySeaLevelPressure = mean(HourlySeaLevelPressure),
    HourlyStationPressure = mean(HourlyStationPressure),
    HourlyVisibility = mean(HourlyVisibility),
    HourlyWetBulbTemperature = mean(HourlyWetBulbTemperature), 
    HourlyWindDirection = mean(HourlyWindDirection), 
    HourlyWindGustSpeed = mean(HourlyWindGustSpeed), 
    HourlyWindSpeed = mean(HourlyWindSpeed)
    
    )

```




### MWRA Non-CSO

```{r}
#READ DATA IN


CR_bacteria <- read_sheet('https://docs.google.com/spreadsheets/d/1V1DJc4er2gctuRN2bv3u3Db0bGxz566ec8j6xmXFZ70/edit?usp=sharing', range = 'cr_bacteria')

CR_secchi <- read_sheet('https://docs.google.com/spreadsheets/d/1fW4_60i-SYkdTPlFQQdN0b5nlZirc2uQyjDN_dvWA18/edit?usp=sharing', range = 'cr_secchi')

CR_physical <- read_sheet('https://docs.google.com/spreadsheets/d/1P5kzPHFABPTKffxM2yQBTIQWq9NAmnGd3PF6kOsSFNU/edit?usp=sharing', range = 'cr_physical')

CR_nutrients <- read_sheet('https://docs.google.com/spreadsheets/d/1kPHmgJUHF7GtNJJDme_gWgB7hTS7i6SE7pqazChKMZ4/edit?usp=sharing')

```

```{r}
#NEW NAMES 
## CRBacteria 
Bacteria_new_names <- c(
  "Project_ID",
  "Region",
  "Subregion",
  "DEP_Segment",
  "Station ID",
  "Date",
  "Depth_category",
  "Sample_depth",
  "Enterococcus",
  "Enterococcus_condition",
  "E_coli",
  "E_coli_condition",
  "coliform",
  "coliform_condition",
  "Rainfall_1d",
  "Rainfall_2d",
  "Rainfall_3d"
)

#CRSECCHI
Secchi_new_names <- c(
  "Project ID",
"Region",
"Subregion",
"DEP Segment",
"Station ID",
"Surface or Bottom",
"Depth to bottom (m)",
"Sample depth for TSS (m)",
"Date",
"Total Suspended Solids (mg/L)",
"Total Suspended Solids '<' or '>'",
"Secchi disk depth (m)"
)


#CRPHYSICAL
Physical_new_names <- c(
"Project ID",
"Region",
"Subregion",
"DEP segment",
"Station ID",
"Surface or Bottom",
"Date",
"Depth of measurement (m)",
"Temperature (C)",
"Salinity (PSU)",
"Specific Conductance (mS/cm)",
"Dissolved Oxygen (mg/L)",
"DO Pct Saturation (%)",
"pH",
"Turbidity (NTU)")



#CRNUTRIENTS
Nutrients_new_names <- c(

"Project ID",
"Region",
"Subregion",
"DEP segment",
"Station ID",
"Date",
"Surface or Bottom",
"Sample depth (m)",
"Ammonium (uM)",
"Ammonium '<' or '>'",
"Nitrate+nitrite (uM)",
"Nitrate+nitrite  '<' or '>'",
"Total dissolved N (uM)",
"Total dissolved N  '<' or '>'",
"Particulate nitrogen (uM)",
"Particulate nitrogen  '<' or '>'",
"Total Kjeldahl Nitrogen (uM)",
"TKN '<' or '>'",
"Phosphate (uM)",
"Phosphate '<' or '>'",
"Total dissolved P (uM)",
"Total dissolved P '<' or '>'",
"Particulate P (uM)",
"Particulate P '<' or '>'",
"Total phosphorus (uM)",
"Total phosphorus '<' or '>'",
"Particulate carbon (uM)",
"Particulate carbon     '<' or '>'",
"Chlorophyll a (ug/L)",
"Chlorophyll '<' or '>'",
"Phaeophytin (ug/L)",
"Phaeophytin '<' or '>'"
)

#Initial Data Wrangle 

#CRBACTERIA
#colnames(CR_bacteria) <- as.character(CR_bacteria[5,]) #set header
#CR_bacteria <- CR_bacteria[-c(1:5), ] #Remove 1st 5 Rows
#rename columns

CR_bacteria <- CR_bacteria %>% 
  set_names(Bacteria_new_names) %>%
  mutate(Date = map_vec(Date,as.Date))


#CR SECCHI

#colnames(CR_secchi) <- as.character(CR_secchi[5,]) #set header
#CR_secchi <- CR_secchi[-c(1:5), ] #Remove 1st 5 Rows
#rename columns

CR_secchi <- CR_secchi %>% 
  set_names(Secchi_new_names) %>%
  mutate(Date = map_vec(Date,as.Date))


#CRPHYSICAL

#colnames(CR_physical) <- as.character(CR_physical[5,]) #set header
#CR_physical <- CR_physical[-c(1:5), ] #Remove 1st 5 Rows
#rename columns

CR_physical <- CR_physical %>% 
  set_names(Physical_new_names) %>%
  mutate(Date = map_vec(Date,as.Date))

#CRNUTRIENTS
#colnames(CR_nutrients) <- as.character(CR_nutrients[5,]) #set header
#CR_nutrients <- CR_nutrients[-c(1:5), ] #Remove 1st 5 Rows
#rename columns

CR_nutrients <- CR_nutrients %>% 
  set_names(Nutrients_new_names) %>%
  mutate(Date = map_vec(Date,as.Date))


```


```{r}

#SITE SELECTION

#CR_bacteria
CR_bacteria_011 <- subset(CR_bacteria, CR_bacteria$`Station ID` == "011")


#CR_nutrients

CR_nutrients_166 <- subset(CR_nutrients, CR_nutrients$`Station ID` == "166")

#CR_physical
CR_physical_011 <- subset(CR_physical, CR_physical$`Station ID` == "011")


#CR_secchi

CR_secchi_011 <- subset(CR_secchi, CR_secchi$`Station ID` == "011")

#AGGREGATE DAILY

#CR_bacteria

ag_CR_bacteria <-CR_bacteria_011 %>%
   group_by(Date) %>%
  summarise(Enterococcus = mean(Enterococcus), E_coli = mean(E_coli), coliform = mean(coliform))

#CR_nutrients

ag_CR_nutrients <- CR_nutrients_166 %>%
   group_by(Date) %>%
  summarise(`Ammonium (uM)` = mean(`Ammonium (uM)`), `Nitrate+nitrite (uM)` = mean(`Nitrate+nitrite (uM)`), `Phosphate (uM)` = mean(`Phosphate (uM)`), `Total phosphorus (uM)` = mean(`Total phosphorus (uM)`, `Chlorophyll a (ug/L)` = mean(`Chlorophyll a (ug/L)`, `Phaeophytin (ug/L)` = mean(`Phaeophytin (ug/L)`)) ))


#CR_physical

ag_CR_physical <-CR_physical_011 %>%
   group_by(Date) %>%
  summarise(`Temperature (C)` = mean(`Temperature (C)`), `Salinity (PSU)` = mean(`Salinity (PSU)`), `Specific Conductance (mS/cm)` = mean(`Specific Conductance (mS/cm)`), `Dissolved Oxygen (mg/L)` = mean(`Dissolved Oxygen (mg/L)`), `DO Pct Saturation (%)` = mean(`DO Pct Saturation (%)`), `pH` = mean(`pH`), `Turbidity (NTU)` = mean(`Turbidity (NTU)`) ) 
            


#CR_secchi

ag_CR_secchi <-CR_secchi_011 %>%
   group_by(Date) %>%
  summarise(`Total Suspended Solids (mg/L)`= mean(`Total Suspended Solids (mg/L)`), `Secchi disk depth (m)` = mean(`Secchi disk depth (m)`))





```




###CAMCSO

```{r}

CAM2015CSO <- read_sheet('https://docs.google.com/spreadsheets/d/11v15YsnizQBilaTK-mzJWz-qp1PLJGqQwrxQ2AV7WdA/edit?usp=sharing', sheet = '2015CAMCSO')


CAM2016CSO <- read_sheet('https://docs.google.com/spreadsheets/d/11v15YsnizQBilaTK-mzJWz-qp1PLJGqQwrxQ2AV7WdA/edit?usp=sharing', sheet = '2016CAMCSO')

CAM2016CSO <- subset(CAM2016CSO, select = c("Date", "CAM017* (MG)"))



CAM2017CSO <- read_sheet('https://docs.google.com/spreadsheets/d/11v15YsnizQBilaTK-mzJWz-qp1PLJGqQwrxQ2AV7WdA/edit?usp=sharing', sheet = '2017CAMCSO')


CAM2017CSO <- subset(CAM2017CSO, select = c("Date", "CAM017* (MG)"))




CAM2018CSO <- read_sheet('https://docs.google.com/spreadsheets/d/11v15YsnizQBilaTK-mzJWz-qp1PLJGqQwrxQ2AV7WdA/edit?usp=sharing', sheet = '2018CAMCSO')


CAM2018CSO <- subset(CAM2018CSO, select = c("Date", "CAM017* (MG)"))

CAM2019CSO <- read_sheet('https://docs.google.com/spreadsheets/d/11v15YsnizQBilaTK-mzJWz-qp1PLJGqQwrxQ2AV7WdA/edit?usp=sharing', sheet = '2019CAMCSO')



CAM2019CSO <- subset(CAM2019CSO, select = c("Date", "CAM017* (MG)"))

CAM2020CSO <- read_sheet('https://docs.google.com/spreadsheets/d/11v15YsnizQBilaTK-mzJWz-qp1PLJGqQwrxQ2AV7WdA/edit?usp=sharing', sheet = '2020CAMCSO')


CAM2020CSO <- subset(CAM2020CSO, select = c("Date", "CAM017* (MG)"))

CAM2021CSO <- read_sheet('https://docs.google.com/spreadsheets/d/11v15YsnizQBilaTK-mzJWz-qp1PLJGqQwrxQ2AV7WdA/edit?usp=sharing', sheet = '2021CAMCSO')


CAM2021CSO <- subset(CAM2021CSO, select = c("Date", "CAM017* (MG)"))

CAM2022CSO <- read_sheet('https://docs.google.com/spreadsheets/d/11v15YsnizQBilaTK-mzJWz-qp1PLJGqQwrxQ2AV7WdA/edit?usp=sharing', sheet = '2022CAMCSO')

CAM2022CSO <- subset(CAM2022CSO, select = c("Date", "CAM017* (MG)"))


```

```{r}
# Combine all values into a single vector and sort them

library(dplyr)

# Ensure column names are consistent across all data frames
colnames(CAM2015CSO) <- c("Date", "CAM017* (MG)")
colnames(CAM2016CSO) <- c("Date", "CAM017* (MG)")
colnames(CAM2017CSO) <- c("Date", "CAM017* (MG)")
colnames(CAM2018CSO) <- c("Date", "CAM017* (MG)")
colnames(CAM2019CSO) <- c("Date", "CAM017* (MG)")
colnames(CAM2020CSO) <- c("Date", "CAM017* (MG)")
colnames(CAM2021CSO) <- c("Date", "CAM017* (MG)")
colnames(CAM2022CSO) <- c("Date", "CAM017* (MG)")

CAM2015CSO$`CAM017* (MG)` <- as.numeric(CAM2015CSO$`CAM017* (MG)`)
CAM2016CSO$`CAM017* (MG)` <- as.numeric(CAM2016CSO$`CAM017* (MG)`)
CAM2017CSO$`CAM017* (MG)` <- as.numeric(CAM2017CSO$`CAM017* (MG)`)
CAM2018CSO$`CAM017* (MG)` <- as.numeric(CAM2018CSO$`CAM017* (MG)`)
CAM2019CSO$`CAM017* (MG)` <- as.numeric(CAM2019CSO$`CAM017* (MG)`)
CAM2020CSO$`CAM017* (MG)` <- as.numeric(CAM2020CSO$`CAM017* (MG)`)
CAM2021CSO$`CAM017* (MG)` <- as.numeric(CAM2021CSO$`CAM017* (MG)`)
CAM2022CSO$`CAM017* (MG)` <- as.numeric(CAM2022CSO$`CAM017* (MG)`)


# Make sure that the "CAM017* (MG)" column is of type double


CAM017 <- bind_rows(
 CAM2016CSO,
  CAM2017CSO, 
  CAM2018CSO,
  CAM2019CSO,
  CAM2020CSO,
  CAM2021CSO,
  CAM2022CSO,
)


CAM017 <- CAM017 %>% rename(MG = `CAM017* (MG)`)

CAM017_discharges <- subset(CAM017, MG != 0)



```

    
  ### ALL CSOs

```{r}

ag_df_CR$Date <- ag_df_CR$date

ag_df_CR <- ag_df_CR[,-c(1) ]

#rm(CR2023, CR2022, CR2020, CR2021, CR2020, CR2019, CR2018, CR2017, CR2016, CR2015, df_CR)

ag_df_CR2 <- ag_df_CR


#Fix Date Formats of Future Joins
MWRACSOFinal$Date <- format(as.Date(MWRACSOFinal$Date, format=
                           "%m-%d-%Y"         ), "%m-%d-%Y")


ag_df_CR2$Date <- format(as.Date(ag_df_CR2$Date , format=
                           "%Y-%m-%d"          ), "%m-%d-%Y")


#join

All <- merge(MWRACSOFinal, ag_df_CR2, by = "Date", all = TRUE)

# Assuming your date column is named "Date"
All$Date <- as.Date(All$Date, format="%m-%d-%Y")

# Order the data frame by Year, Month, and Day
All <- All[order(year(All$Date), month(All$Date), day(All$Date)), ]

```

Join CAM + CSO

```{r}
All <- merge(All, CAM017, by = "Date", all = TRUE)
All <- All %>%
  rename(CAM017MG = MG)



```

```{r}
All <- na.omit(All)
```



###CCM LOGAN

#HourlyAltimeterSetting


```{r}

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 0, columns = "HourlyAltimeterSetting", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 0, columns = "HourlyAltimeterSetting", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```

#HourlyDryBulbTemperature

```{r}

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyDryBulbTemperature", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyDryBulbTemperature", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```

#HourlyPrecipitation
```{r}

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyPrecipitation", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyPrecipitation", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```

#HourlyPressureChange

```{r}

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyPressureChange", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyPressureChange", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```

#HourlyPressureTendency

```{r}

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyPressureTendency", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyPressureTendency", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```


#HourlyRelativeHumidity

```{r}

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyRelativeHumidity", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = " HourlyRelativeHumidity", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```


#HourlySeaLevelPressure
```{r}

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlySeaLevelPressure", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlySeaLevelPressure", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```


#HourlyStationPressure
```{r}

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyStationPressure", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyStationPressure", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```


#HourlyVisibility
```{r}

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyVisibility", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyVisibility", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```

#HourlyWindDirection
```{r}

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyWindDirection", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyWindDirection", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```

#HourlyWindGustSpeed

```{r}

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyWindGustSpeed", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyWindGustSpeed", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```

#HourlyWindSpeed

```{r}

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyWindSpeed", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyWindSpeed", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```



###CCM EPA BUOY
```{r}
ag_df_CR <- na.omit(ag_df_CR)
```

CCM LibSizes Explained
- CCM is wraps a bunch of straps for doing cross map prediction for subsets of the data
- result is plotted is Cross Map Skill as amount of data used (L library size) 
                  - number of attractor points 

- expect quasi logistic saturation, log spaced 


libSizes - 20 200  10 sequence of libsizes to test, x values in CCM curve
Sample - 
this is where you do bootstrap, subsets of data ex: 100, do 100 n number of random resamples

##PH

```{r}
ph.del.cor <- cor(cmap.ph.del)


# Define a function to calculate correlation
calculate_correlation <- function(row, ref_column) {
  cor(row[-1], ref_column)
}

# Apply the function row-wise
correlations <- apply(cmap.ph.del[, -1], 1, calculate_correlation, cmap.ph.del$LibSize)


# Add correlations to the CMAP data frame
cmap.ph.del$correlations <- correlations


plot(cmap.ph.del)
```


```{r}

cmap.ph.del <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "ph", target = "del_phy", libSizes = "20 200 10", sample = 10, showPlot = TRUE)

ph.del.cor <- cor(cmap.ph.del)

plot.cmap.ph.del <- plot(x = cmap.ph.del$LibSize, y = cmap.ph.del$`ph:del_phy`)
plot(x = cmap.ph.del$LibSize, y = cmap.ph.del$`ph:del_phy`, type = "l",
     main = "Line Plot", xlab = "LibSize", ylab = "ph:del_phy")

# Add a line to the plot
lines(x = cmap.ph.del$LibSize, y = cmap.ph.del$`ph:del_phy`, col = "red")


abline(h = 0.8738390, col = "red")

  

correlations <- apply(cmap.ph.del , 1, function(x) cor(x, CMAP))

cmap.ph.del + geom_abline(slope = 0.8738390, intercept = 0, color = "red")

# Extract the ggplot object from the CCM plot
ggplot_obj <- as.ggplot(CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "ph", target = "del_phy", libSizes = "20 200 10", sample = 10, showPlot = TRUE))

# Modify the ggplot object as needed
ggplot_obj + geom_hline(yintercept = 0.8738390, color = "red")
plot.new<- cmap.ph.del + abline(y = 0.8738390, color = "red")



cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "ph", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "ph", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE) 


```
```{r}


cmap.ph.del <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "ph", target = "del_phy", libSizes = "20 200 10", sample = 10, showPlot = TRUE, abline())

```




#using simplex 

```{r}

lib_ins <- c(1,992) # data up through end of 2022; this is the training set
lib_oos <- c(993,1138) # leave this alone until we're nearly done with the project

cmap <- Simplex(dataFrame = ag_df_CR, lib = lib_ins, pred = lib_ins, target = "del_phy", columns = "ph", Tp = 0, E = 4)

head(cmap)
plot(cmap)


ag_df_CRPredict <- Simplex(dataFrame = ag_df_CR, pred = "1076 1223", target = "chl",
columns = "chl", E = 4)

cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "ph", target = "del_phy", , sample = 10, showPlot = TRUE)

```



##Celsius

```{r}

cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "Celsius", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "Celsius", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```

##SPCOND

```{r}

cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "spcond", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "spcond", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```

#DO

```{r}

cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "do", target = "del_phy", libSizes = "20 200 10 ", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "do", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE) 


cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "do", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```


#TURB

```{r}

cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "turb", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE) 

cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "turb", target = "del_phy", libSizes = "20 200 10", sample = 10, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "turb", target = "chl", libSizes = "20 200 10", sample = 10, showPlot = TRUE)



```

#CHL, PHY DEL_PHY

```{r}

cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "chl", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE) 

cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "chl", target = "del_phy", libSizes = "20 200 10", sample = 10, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0, columns = "phy", target = "del_phy", libSizes = "20 200 10", sample = 10, showPlot = TRUE)



```


#Salinity

```{r}

cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0 columns = "Salinity", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_df_CR, E = 4, Tp = 0 columns = "Salinity", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```


#CCM CAMCSO

Need to use the same data?
```{r}

cmap <- CCM(dataFrame = All, E = 4, Tp = 0, columns = "MG", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = All, E = 4, Tp = 0, columns = "MG", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


```


#CCM MWRA Non-CSO

***CR_bacteria***


#Enteroccus 
```{r}


cmap <- CCM(dataFrame = ag_CR_bacteria, E = 0, Tp = 0, columns = "Enteroccus", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_CR_bacteria, E = 0, Tp = 0, columns = "Enteroccus", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


```

#E_coli 

```{r}


cmap <- CCM(dataFrame = ag_CR_bacteria, E = 4, Tp = 4, columns = "E_coli", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_CR_bacteria, E = 4, Tp = 4, columns = "E_coli", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


```

***CR_Secchi***



#Total Suspended Solids (mg/L)

```{r}


cmap <- CCM(dataFrame = ag_CR_secchi, E = 4, Tp = 4, columns = "Total Suspended Solids (mg/L)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_CR_secchi, E = 4, Tp = 4, columns = "Total Suspended Solids (mg/L)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


```

***CR_Nutrients ***

#Ammonium (uM)


```{r}


cmap <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Ammonium (uM)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Ammonium (uM)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


```

#"Nitrate+nitrite (uM)"

```{r}


cmap <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Nitrate+nitrite (uM)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Nitrate+nitrite (uM)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


```

#Phosphate (uM)   

```{r}


cmap <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Phosphate (uM)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Phosphate (uM)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


```

#Total phosphorus (uM)
```{r}


cmap <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Total phosphorus (uM)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Total phosphorus (uM)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


```
ccm uses y to predict x, if true, x can affect y 
ccm wraps (Simplex target = x, columns = y)



multivariate 
Simplex ( Embedded = True, columns = c("x1, "x2)) 
set CCM samples to 10 to see result 
